Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-06-02 manuscript.Rmd
adjusted ordination figure

```{r ordinations, echo=FALSE, fig.cap="FRE", message=FALSE, warning=FALSE, out.width="100%"}
knitr::include_graphics(here("figures", "ord_plots.png"))
```

>>>>

```{r ordinations, echo=FALSE, fig.cap="a. plsr ordination scores all samples diff fresh vs fossil b. regression coef; PC1 c. regression coef PC2; d plsr ordination scores only samples from cores diff spt vs acet; e. regression coef PC1; f. regression coef PC2", message=FALSE, warning=FALSE, out.width="100%"}
knitr::include_graphics(here("figures", "ord_plots.png"))
```
